New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/article.tex
nouvelles valeurs
Nouvelle conclusion

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,214 \).

@@

\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

>>>>

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,256 \).

@@

\qquad [OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

\qquad [NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
algorithms based on randomness such as Monte-Carlo algorithms to find better templates.
